title

### 2018-07-17 01_writing/Schratz_hyperspectral.tex
update CV table

The \textit{Pinus radiata} plots of this study, named \textit{Laukiz 1}, \textit{Laukiz 2}, \textit{Luiando} and \textit{Oiartzun}, are located in the northern part of the Basque Country (\autoref{fig:study_area}).
\textit{Oiartzun} has the most observations (n = 529) while \textit{Laukiz 2} has the largest area size (1.44 ha).
All plots besides \textit{Luiando} are located nearby the coast (\autoref{fig:study_area}).
The data collection took place in September 2016.

@@

The airborne hyperspectral data was acquired during two flight campaigns on September 28th and October 5th 2016, both around 12 am.
The images were taken by an AISAEAGLE-II sensor from the \ac{ICGC}.
All preprocessing steps (geometric, radiometric, atmospheric) have been conducted by \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.

Additional data characteristics are provided in Table 1:

@@

Multiple algorithms were benchmarked on predictive performance to find the best performing one.
Besides the well-known \ac{SVM} \citep{Vapnik1998} we also used \textit{xgboost} which is ensemble method relying on the idea of tree boosting that gained a lot of attention in recent years \citep{chenXGBoostScalableTree2016}.
We also added penalized L2 (Ridge) regression to the algorithm collection due to its ability to handle highly correlated covariates.
We also want to explain why we did not consider the probably most popular machine-learning algorithm, Random Forest: Due to the high number of variables model fitting times in the range hours for a single model fit were not practicable for this work. 
These high fitting times are caused by hyperparameter \texttt{mtry} which scales with the number of variables \citep{Probst2018b}.

@@

% Performance estimates
\begin{table}[b!]
	\centering
	\caption[t]{Four-fold spatial \ac{CV} performances of RR, SVM and xgboost using \ac{RMSE} as the error measure. 
	Mean and standard deviation are shown.}
	\begingroup\footnotesize
	\begin{tabular}{llll}
		RR            & SVM           & xgboost \\
		\hline
		59.10 (22.71) & 36.23 (15.73) &  &         \\
		\bottomrule
	\end{tabular}
	\endgroup
	\label{tab:penalty_comparison}
	\end{table}

\begin{table}[t!]
\centering
\caption[t]{Predictive performance of xgboost using the merged dataset (supermodel) and observations on a plot level only (single plot) with \ac{RMSE} as the error measure. The performance estimates for "All Plots" correspond to the fold for which the respective plot was serving as the test set. For "single plot", the values correspond to the mean value of the SpCV at the repetition level (10 folds, 20 repetitions), scored by models fitted on the data of the respective plot only.}
\begingroup\footnotesize
\begin{tabular}{lll}
	\\
	Plot/Data & All Plots (Block CV) & Single plot (SpCV) \\
	\hline
	Laukiz 1  & 58.95                     & 89.89              \\
	Laukiz 2  & 27.94                     & 30.37              \\
	Luiando   & 69.72                     & 76.02              \\
	Oiartzun  & 58.09                     & 106.65             \\ 
	\bottomrule
\end{tabular}
\endgroup
\label{tab:supermodel_performance}
\end{table}

>>>>

The \textit{Pinus radiata} plots of this study, named \textit{Laukiz 1}, \textit{Laukiz 2}, \textit{Luiando} and \textit{Oiartzun}, are located in the northern part of the Basque Country (\autoref{fig:study_area}).
\textit{Oiartzun} has the most observations (n = 529) while \textit{Laukiz 2} has the largest area size (1.44 ha).
All plots besides \textit{Luiando} are located nearby the coast (\autoref{fig:study_area}).
In total 1750 observations are available (\textit{Laukiz 1} = 479, \textit{Laukiz 2} = 451, \textit{Luiando} = 291, \textit{Oiartzun} = 529).
The data was surveyed in September 2016.

@@

The airborne hyperspectral data was acquired during two flight campaigns on September 28th and October 5th 2016, both around 12 am.
The images were taken using a AISAEAGLE-II sensor.
All preprocessing steps (geometric, radiometric, atmospheric) have been conducted by the \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.
Additional metadata information is available in Table 1:

@@

Multiple algorithms were benchmarked on predictive performance to find the best performing one.
Besides the well-known \ac{SVM} \citep{Vapnik1998} we also used \textit{xgboost} which is ensemble method relying on the idea of tree boosting that gained a lot of attention in recent years \citep{chenXGBoostScalableTree2016}.
We also added penalized L2 (Ridge) regression to the algorithm collection due to its ability to handle highly correlated covariates.
The probably most popular machine-learning algorithm, Random Forest, was not considered for this study: Due to the high number of variables, model fitting times in the range hours for a single model fit were not practicable for this work.
These high fitting times are caused by hyperparameter \texttt{mtry} which scales with the number of variables \citep{Probst2018b}.

@@

% Performance estimates
\begin{table}[b!]
\centering
\caption[t]{Four-fold spatial \ac{CV} performances of RR, SVM and xgboost using \ac{RMSE} as the error measure.
	Mean and standard deviation are shown.}
\begingroup\footnotesize
\begin{tabular}{llll}
	RR            & SVM           & xgboost       \\
	\hline
	59.10 (22.71) & 36.23 (15.73) & 33.26 (16.61) \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:penalty_comparison}
\end{table}

\begin{table}[t!]
\centering
\caption[t]{Predictive performance of \textit{xgboost} using all observations (All Observations ) and observations from single plots only (Single Plot Observations) with \ac{RMSE} as the error measure. The performance estimates for "All Observations" correspond to the fold for which the respective plot was serving as the test set. Column "single plot", shows the mean performances at the repetition level of a SpCV (5 folds, 5 repetitions), scored by using data of the respective plot only.}
\begingroup\footnotesize
\begin{tabular}{lll}
	\\
	Plot/Data & All Observations (Block CV) & Single Plot Observations (SpCV)             \\
	\hline
	Laukiz 1  & 22.03                & -                              \\
	Laukiz 2  & 51.75                & 17.37  (update to rep mean!)   \\
	Luiando   & 13.20                & -                              \\
	Oiartzun  & 32.97                & 14.72    (update to rep mean!) \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:supermodel_performance}
\end{table}
